\documentclass[letterpaper,9pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{libertine} % You requested a serif font, so I'm using Linux Libertine which is similar to Liberation Serif
\usepackage{setspace}
\pagestyle{empty} % Remove page number

\begin{document}

% Set line spacing to 0.9 (slightly reduced)
\setstretch{0.9}

% Contact Information
\begin{center}
\textbf{\Large Jacob Hemmerich} \\
ADDRESS GOES HERE \\
Phone: GOES HERE \\
Email: GOES HERE \\
Website: www.hemmerich.co
\end{center}

% Experience
\section*{Experience}
\begin{itemize}
\item[] \textbf{Von Maur, Davenport, IA — Computer Hardware Support} \\
\textit{September 2023 - Present} \\
Deployed Windows computers, iOS, \& Android devices, ensuring seamless functionality. Configured Cisco phones in CUCM, mailbox accounts in Exchange, and administered AS/400 sessions. Partnered with software engineers and service providers to maximize reliability.

\item[] \textbf{Citi, San Antonio, TX — Service Rep IV} \\
\textit{February 2023 - September 2023} \\
Managed accounts for an international portfolio of retail branded consumer and commercial credit cards. Performed end-to-end servicing for accounts including promotions, disputes, and store calls. Lead focus groups and town halls to improve business solutions.

\item[] \textbf{FNBO, Omaha, NE — Senior Disputes Specialist} \\
\textit{February 2020 - December 2022} \\
Handled second tier support calls and chargeback processing for thousands of Visa and Mastercard credit card disputes. Performed follow-ups and coaching with junior staff to create exceptional customer experiences. Maintained daily production reports from a variety of data sets including TRIPS and Avaya phone skills using Excel VBA/Macros.

\item[] \textbf{Iowa State University Extension, Ames, IA— Computer Support Specialist} \\
\textit{August 2018 - January 2020} \\
Processed hundreds of complex end-user computer support tickets. Developed technical documentation used by colleagues across Iowa’s 99 counties. Collaborated on the deployment of a statewide Cisco Meraki networking stack.
\end{itemize}

% Education
\section*{Education}
\begin{itemize}
\item[] \textbf{University of Nebraska - Omaha, Omaha, NE— B.S. in Management Information Systems} \\
\textit{January 2020 - Present}

\item[] \textbf{Thomas Jefferson High School, Council Bluffs, IA — High School} \\
\textit{Class of 2017}
\end{itemize}

% Featured Project
\section*{Featured Project}
\textbf{Homelab — Home Server Project} \\
Maintained an Alpine Linux based home server hosting Docker containers including cgit, Jellyfin, nginx, xmpp, and Wireguard. Supported access control for dozens of users with OpenLDAP.

% Skills
\section*{Skills}
\begin{itemize}
    \item Mastery of business \& IT software including Jira, Office, Salesforce, AirWatch and ServiceNow
    \item Proficiency in banking and business privacy rules and regulations, including Regulations Z and E, FCRA, and BSA
\end{itemize}

% Activities
\section*{Activities}
\begin{itemize}
    \item Volunteer, Citibank Angel Day
    \item Volunteer, San Antonio Food Bank
    \item Club Member, Lake Itasca Region Pioneer Farmers
    \item Virtual Campus Tour Guide, University of Nebraska Omaha
    \item President, Systems Development Club at Iowa State University
    \item Sustainability Chair, Bennet Hall at Iowa State University
\end{itemize}

\end{document}
